---
title: "Predicting Vulnerability"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
rootdir <- dirname(getwd())
```

```{r}
library(tidyverse)
gamma <- 3.23
beta <- .9
R <- 1.013
cbar <- .42
lambda <- .85
sigma <- 3.95
mus <- seq(8.5,13,.01)
source(paste(rootdir, "/code/VFIfunctions.R", sep = ""))
Vlist <- readRDS(paste(rootdir, "/data/model_output/Vlist1.rds", sep = ""))
df.wtps <- readRDS(paste(rootdir, "/data/model_output/df_wtps1.rds", sep = ""))
```

Checking results

```{r}
## Market clearing
sum(df.wtps$bsx_pre + df.wtps$quake_aid - df.wtps$food_consumption, na.rm = TRUE)

## PDFs
bsx = lapply(df.wtps$hhid, bufferstock, Vlist, df.wtps)
cdist_pre = unlist(lapply(bsx, function(x) x[1]))
cdist_post = unlist(lapply(bsx, function(x) x[2]))
thresholds <- seq(40000, 200000, 20000)
pdf_pre = unlist(lapply(thresholds, function(x) sum(cdist_pre < x)/length(cdist_pre)))
pdf_post = unlist(lapply(thresholds, function(x) sum(cdist_post < x)/length(cdist_post)))
pdfmoments_t <- c(0, 0, 0, .04, .25, .52, .64, .77, .86)
pdfmoments_u <- c(0.05, 0.18, 0.32, 0.57, 0.63, 0.77, 0.79, 0.86, 0.92)

df.moments <- data.frame("pxc" = c(pdf_pre, pdf_post, pdfmoments_u, pdfmoments_t),
                         "mod" = c(rep("Modeled", length(c(pdf_pre, pdf_post))), rep("Empirical", length(c(pdfmoments_u, pdfmoments_t)))),
                         "aid" = c(rep("Untreated", length(pdf_pre)), rep("Treated", length(pdf_post)),
                                   rep("Untreated", length(pdfmoments_u)), rep("Treated", length(pdfmoments_t))),
                         "thresh" = rep(thresholds, 4)) 

ggplot(df.moments) +
  geom_line(aes(x = thresh, y = pxc, color = mod, linetype = aid)) +
  theme_bw() + theme(text = element_text(size = 20)) +
  labs(x = "C", y = "P(Food consumption < C)", linetype = "", color = "")
ggsave(paste(rootdir, "/presentation_materials/matchedmoments.png", sep = ""), width = 10, height = 7)
```

Show sample value function and consumption function

```{r}
mu <- median(df.wtps$mu)
i <- which(unlist(lapply(Vlist, function(x) x$mu))==mu)
Vfx <- Vlist[[i]]$Vfx
cfx <- Vlist[[i]]$cfx
xgrid <- Vlist[[i]]$xgrid
wtpc <- unlist(lapply(xgrid, wtpcurve, mu = mu, amt = 100000))

ggplot() + geom_line(aes(x = xgrid, y = Vfx(xgrid))) +
  labs(x = "Buffer Stock (x_it)", y = "V(x)", title = "Value Function") + 
  theme_bw() + xlim(min(xgrid), 1e6) + theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/vfx.png", sep = ""), width = 10, height = 7)

ggplot() + geom_line(aes(x = xgrid, y = cfx(xgrid))) +
  labs(x = "Buffer Stock (x_it)", y = "c(x)", title = "Policy Function") + 
  theme_bw() + xlim(min(xgrid), 1e6) + ylim(0, 2.5e5) + theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/cfx.png", sep = ""), width = 10, height = 7)

ggplot() + geom_line(aes(x = xgrid, y = cfx(xgrid+100000) - cfx(xgrid))) +
  labs(x = "Buffer Stock (x_it)", y = "c(x + a) - c(x)", title = "Effect of 100k Aid on Consumption") + 
  theme_bw() + xlim(min(xgrid), 1e6) + theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/efxaid.png", sep = ""), width = 10, height = 7)

ggplot() + geom_line(aes(x = xgrid, y = wtpc)) +
  labs(x = "Buffer Stock (x_it)", y = "WTP(x)", title = "Willingness to Pay for 100k Aid") + 
  theme_bw() + theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/wtpcurve.png", sep = ""), width = 10, height = 7)
```

Plot a bunch of functions

```{r}
vfxlist <- function(x){
  f = x$Vfx
  xs = x$xgrid
  fx = f(xs)
  mu = rep(x$mu, length(xs))
  return(cbind(xs, fx, mu))
}

l <- lapply(Vlist, vfxlist)
df.vlist <- as.data.frame(do.call(rbind, l))

topV  = approxfun(x = df.vlist$xs[df.vlist$mu==10.5], y = df.vlist$fx[df.vlist$mu==10.5])

ggplot(filter(df.vlist, mu %in% seq(9.8, 10.5, by = .02), between(xs, -2000, 100000))) + 
  geom_segment(aes(x = 0, y = -Inf, xend = 0, yend = topV(0)), color = "red") +
  geom_segment(aes(x = 0, y = topV(0), xend = 100000, yend = topV(0)), color = "red") + 
  geom_line(aes(x = xs, y = fx, color = mu, group = mu)) +
  theme_bw() + theme(text = element_text(size = 20)) + 
  labs(x = "Buffer Stock (x_it)", y = "V(x|mu)", title = "Equivalent Variation for 100k Aid")
ggsave(paste(rootdir, "/presentation_materials/equivar.png", sep = ""), width = 10, height = 7)
```

### Predicting Vulnerability

Histogram of WTPs

```{r}
ggplot() + geom_histogram(aes(x = df.wtps$wtp), bins = 100) + 
  geom_vline(aes(xintercept = 100000), color = "red") +
  theme_bw() + theme(text = element_text(size = 20)) + 
  labs(x = "Willingness to Pay for 100k")
ggsave(paste(rootdir, "/presentation_materials/wtphist.png", sep = ""), width = 10, height = 7)

ggplot() + geom_histogram(aes(x = df.wtps$bsx_pre), bins = 100) + 
  theme_bw() + theme(text = element_text(size = 20)) + 
  labs(x = "Pre aid buffer stock")

ggplot(df.wtps) + geom_point(aes(x = food_consumption, y = wtp)) + 
  geom_hline(aes(yintercept = 100000), color = "red") +
  theme_bw() + theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/wtpvsfood.png", sep = ""), width = 10, height = 7)

ggplot(df.wtps) + geom_point(aes(x = bsx_pre, y = wtp)) + 
  geom_hline(aes(yintercept = 100000), color = "red") +
  theme_bw() + theme(text = element_text(size = 20)) 
```

Actual WTP

```{r}
## fraction receiving aid
af <- weighted.mean(df.wtps$quake_aid_bin, df.wtps$wt_hh)
af
## avg WTP
a <- weighted.mean(df.wtps$wtp, df.wtps$wt_hh, na.rm = TRUE)
a
## WTP for those receiving aid
b <- weighted.mean(df.wtps$wtp[df.wtps$quake_aid_bin==1], df.wtps$wt_hh[df.wtps$quake_aid_bin==1], na.rm = TRUE)
b
## WTP for those receiving NGO aid
c <- weighted.mean(df.wtps$wtp[df.wtps$NGO_transfers>0], df.wtps$wt_hh[df.wtps$NGO_transfers>0], na.rm = TRUE)
c
```

- heterogeneity by district
- heterogeneity by wave

Perfect targeting Benchmark - and value of tech that could get you there

```{r}
qt <- quantile(df.wtps$wtp, probs = 1-af, na.rm = TRUE)
qt

weighted.mean(df.wtps$wtp[df.wtps$wtp>qt], df.wtps$wt_hh[df.wtps$wtp>qt], na.rm = TRUE)
```


Remote sensing Allocations
- everyone in village

```{r}
q <- quantile(df.wtps$UFchg_500m, probs = af, na.rm = TRUE)

d <- weighted.mean(df.wtps$wtp[df.wtps$UFchg_500m<q], df.wtps$wt_hh[df.wtps$UFchg_500m<q], na.rm = TRUE)
d
```

-Highest WTPs within villages

```{r}
## Fraction of villages damaged
vd <- weighted.mean(df.wtps$UFchg_500m<0, df.wtps$wt_hh, na.rm = TRUE)

## Percent of individuals in those villages that can get aid holding budget constant
p <- af/vd

## WTP cutoff
q <- quantile(df.wtps$wtp[df.wtps$UFchg_500m<0], p, na.rm = TRUE)

e <- weighted.mean(df.wtps$wtp[df.wtps$UFchg_500m < 0 & df.wtps$wtp > q], df.wtps$wt_hh[df.wtps$UFchg_500m<0 & df.wtps$wtp >q], na.rm = TRUE)
e

scenarios <- factor(c("Received Aid", "Received NGO Aid", "Remote Sensing Villages", "Remote Sensing +"), 
                    levels = c("Received Aid", "Received NGO Aid", "Remote Sensing Villages", "Remote Sensing +"))
relativeperf <- sapply(c(b,c,d,e), function(x) x/a - 1)

ggplot() +
  geom_col(aes(y = relativeperf, x = scenarios, fill = c(1,2,3,4))) +
  theme_bw() + theme(text = element_text(size = 20), legend.position = "none") + 
  labs(y = "", x = "", title = "% Increased WTP over random allocation")
ggsave(paste(rootdir, "/presentation_materials/counterfactuals.png", sep = ""), width = 12, height = 7)
```

Confusion matrices - Actual Allocation

```{r}
tclass <- c("Low WTP", "Low WTP", "High WTP", "High WTP")
pclass <- c("Received Aid", "No Aid", "Received Aid", "No Aid")

y <- c(sum(df.wtps$wt_hh[df.wtps$quake_aid_bin==1 & df.wtps$wtp < qt], na.rm = TRUE)/sum(df.wtps$wt_hh[!is.na(df.wtps$wtp)]),
       sum(df.wtps$wt_hh[df.wtps$quake_aid_bin==0 & df.wtps$wtp < qt], na.rm = TRUE)/sum(df.wtps$wt_hh[!is.na(df.wtps$wtp)]),
       sum(df.wtps$wt_hh[df.wtps$quake_aid_bin==1 & df.wtps$wtp > qt], na.rm = TRUE)/sum(df.wtps$wt_hh[df.wtps$wtp > qt], na.rm = TRUE),
       sum(df.wtps$wt_hh[df.wtps$quake_aid_bin==0 & df.wtps$wtp > qt], na.rm = TRUE)/sum(df.wtps$wt_hh[df.wtps$wtp > qt], na.rm = TRUE))

labs <- c("FP/N \n", "TN/N \n", "TP/P \n", "FN/P \n")

ggplot() +
  geom_tile(aes(x = ordered(pclass, levels = unique(pclass)), y = ordered(tclass, levels = unique(tclass)), fill = y)) +
  geom_text(aes(x = ordered(pclass, levels = unique(pclass)), y = ordered(tclass, levels = unique(tclass)), 
                label = paste(labs, round(y,3))), color = "white") + 
  theme_bw() + guides(fill = FALSE) + labs(x = "", y = "", title = "Actual Allocations") +
  theme(text = element_text(size = 22))
ggsave(paste(rootdir, "/presentation_materials/confmat.png", sep = ""), width = 10, height = 7)
```

