---
title: "WB HRVS estimation"
author: "Matthew Gordon"
date: "7/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
rootdir <- dirname(getwd())
```

### Load packages and data

```{r, message=FALSE, echo=FALSE, warning=FALSE}
library(tidyverse)
library(sf)
library(lfe)
library(AER)
library(ggnewscale)
library(cowplot)
library(stargazer)
library(sandwich)
library(readstata13)
#devtools::install_github("mdgordo/rdrobust",ref="master")
library(rdrobust)
#devtools::install_github("mdgordo/dumbells",ref="master")
library(dumbells)
library(rdpower)
library(boot)
library(parallel)
source(paste(rootdir, "/code/rdhelpers.r", sep = ""))

df.hh <- read_csv(paste(rootdir, "/data/processed/full_panel.csv", sep = ""), guess_max = 7500)
df.hh <- filter(df.hh, !is.na(income_gross) & income_gross>0 & food_consumption>0)
```

Define vars

```{r}
placebos <- c("elevation", "shake_pga", "gorkha_hh", "gorkha_loss_ever", "high_caste", "age_hh", "highest_ed", 
              "always_lived_house", "always_lived_dist", "slope", "pub_transfers", "NGO_transfers")
infravars <- c("time_to_bank", "time_to_school", "time_to_health")
aidvars <- c("aid_cumulative_bin", "aid_cumulative")
numvars <- c("currentlyliving", "under5", "under18", "over65", "femalehh", "extended_members", "children_attending")
consumptionvars <- c("food_consumption", "durables_consumption", "home_investment", "transportation", "energy_utilities", "ceremonial_expenses", "other_consumption")
incomevars <- c("remittance_income", "annual_wages", "ag_livestock_income", "pub_transfers", "inputs")
percapitavars <- c("income_pc", "consumption_pc", "food_consumption_pc")
pricevars <- c("chicken_price", "rice_price", "lentil_price", "sugar_price", "mutton_price")
assetvars <- c("livestock_sales", "livestock_purchases", "loans_taken_past_year", "loan_payments", "total_outlays_net")
shockvars <- c("natural_shocks", "market_shocks", "idiosyncratic_shocks")
copingvars <- c("dissaving", "felt_hunger", "school_interrupt", 
                "child_labor", "child_days_worked", "child_wage_days", "n_migrants")
```

#### Regression Discontinuity

### MSE bandwidths - Cattaneo paper
Can try also with aid_total - similar

```{r, warning=FALSE}
bws <- rbind(optbw("aid_cumulative_bin", b = "dist_2_seg13", df = df.hh, dist.exclude = "none", wide = TRUE),
      optbw("food_consumption", b = "dist_2_seg13", df = df.hh, fuzzy = TRUE, dist.exclude = "none", wide = TRUE))

h0 <- bws[2,1]
b0 <- bws[2,3]
```

Power calculations

```{r, warning = FALSE}
df.pow <- filter(df.hh, !is.na(consumption) & designation!="none", 
                 !is.na(high_caste), !is.na(class5), !is.na(age_hh), !is.na(gorkha_hh), !is.na(slope), !is.na(elevation))
powcovs <- covmatmaker("dist_2_seg13", df.pow, wide = TRUE)

df.pow <- mutate(df.pow, fcs60 = if_else(food_consumption < 60000, 1, 0),
                fcs100 = if_else(food_consumption < 100000, 1, 0),
                fcs200up = if_else(food_consumption < 200000, 0, 1))

print("First Stage")
a <- rdpower(data = cbind(df.pow$aid_cumulative_bin, df.pow$dist_2_seg13), h = h0, b = b0, kernel = "triangular", vce = "hc1", 
        covs =  powcovs, cluster = df.pow$strata, weights = df.pow$wt_hh, tau = .27)
print("Consumption")
a <- rdpower(data = cbind(df.pow$food_consumption, df.pow$dist_2_seg13), h = h0, b = b0, kernel = "triangular", vce = "hc1", 
        covs =  powcovs, cluster = df.pow$strata, weights = df.pow$wt_hh)
print("Consumption w IV")
a <- rdpower(data = cbind(df.pow$food_consumption, df.pow$dist_2_seg13), h = h0, b = b0, kernel = "triangular", vce = "hc1", 
        covs =  powcovs, cluster = df.pow$strata, weights = df.pow$wt_hh, fuzzy = df.pow$aid_cumulative_bin)
print("Consumption Dummies")
a <- rdpower(data = cbind(df.pow$fcs60, df.pow$dist_2_seg13), h = h0, b = b0, kernel = "triangular", vce = "hc1", 
        covs =  powcovs, cluster = df.pow$strata, weights = df.pow$wt_hh, fuzzy = df.pow$aid_cumulative_bin)

a <- rdpower(data = cbind(df.pow$fcs100, df.pow$dist_2_seg13), h = h0, b = b0, kernel = "triangular", vce = "hc1", 
        covs =  powcovs, cluster = df.pow$strata, weights = df.pow$wt_hh, fuzzy = df.pow$aid_cumulative_bin)

a <- rdpower(data = cbind(df.pow$fcs200up, df.pow$dist_2_seg13), h = h0, b = b0, kernel = "triangular", vce = "hc1", 
        covs =  powcovs, cluster = df.pow$strata, weights = df.pow$wt_hh, fuzzy = df.pow$aid_cumulative_bin)
```

### Functions for Mccrary test
Discrete version based on: https://cattaneo.princeton.edu/aie-rdd/Frandsen_2016_AIE.pdf
Sampling frame based on 2010 census - need to adjust to hhs per unit area

```{r}
mcplot <- histfunc("dist_2_seg13", filter(df.hh, wave==1), h = h0, dist.exclude = "none")

mcplot + labs(x = "distance to border") + theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/mccrary.png", sep = ""), width = 10, height = 7)
```

### RD plots

### Aid vars

```{r, message=FALSE, warning=FALSE}
plotlist <- lapply(aidvars, plotvar, b = "dist_2_seg13", h=h0, df = df.hh, dist.exclude = "none", wide = TRUE)
plotlist

p2 = plotlist[[1]] +
  labs(x = "distance to border", y = "residualized fraction receiving aid") +
  theme(text = element_text(size = 20)) + ylim(-.5,.5)
p2
ggsave(paste(rootdir, "/presentation_materials/aid_bin.png", sep = ""), width = 10, height = 7) 

plotlist[[2]] +
  labs(x = "distance to border", y = "Amount Received") +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/aid_amt.png", sep = ""), width = 10, height = 7) 

```

### Placebo tests

```{r, message=FALSE, warning=FALSE}
plotlist <- lapply(placebos[!placebos %in% c("elevation", "shake_pga", "slope")], plotvar, b = "dist_2_seg13", h=h0, 
                   df = df.hh, dist.exclude = "none")
plotlist
p1 = plotlist[[2]] +
  labs(x = "distance to border", y = "residualized reported earthquake losses") +
  theme(text = element_text(size = 20))
p1
ggsave(paste(rootdir, "/presentation_materials/losses_placebo.png", sep = ""), width = 10, height = 7)

plotlist[[9]] +
  labs(x = "distance to border", y = "residualized NGO aid") +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/NGO_placebo.png", sep = ""), width = 10, height = 7)


cowplot::plot_grid(p2, p1)
ggsave(paste(rootdir, "/presentation_materials/aidanddamage.png", sep = ""), width = 13, height = 7) 
```

```{r, message=FALSE, warning=FALSE}
lapply(infravars, plotvar, b = "dist_2_seg13", h=h0, df = df.hh, dist.exclude = "none", wide = TRUE)
lapply(pricevars, plotvar, b = "dist_2_seg13", h=h0, df = df.hh, dist.exclude = "none", wide = TRUE)
```


## HH Composition

```{r}
plotlist <- lapply(numvars, plotvar, b = "dist_2_seg13", h=h0, df = df.hh, dist.exclude = "none", wide = TRUE)
plotlist

plotlist[[1]] +
  labs(x = "distance to border", y = "Currently Living in HH") +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/currentlyliving.png", sep = ""), width = 10, height = 7)

plotlist[[5]] +
  labs(x = "distance to border", y = "Female Headed Household") +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/FHH.png", sep = ""), width = 10, height = 7)

```

## Consumption

```{r}
plotlist <- lapply(consumptionvars, plotvar, b = "dist_2_seg13", h=h0, df = df.hh, ihs=FALSE, dist.exclude = "none", wide = TRUE)
plotlist

plotlist[[1]] +
  labs(x = "distance to border", y = "Food Consumption") +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/food.png", sep = ""), width = 10, height = 7)
```

## Income

```{r, message=FALSE, echo=FALSE, warning=FALSE}
plotlist <- lapply(incomevars, plotvar, b = "dist_2_seg13", h=h0, df = df.hh, ihs=FALSE, dist.exclude = "none", wide = TRUE)
plotlist

plotlist[[1]] +
  labs(x = "distance to border", y = "Remittances") +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/remittances.png", sep = ""), width = 10, height = 7)
incomevars
```

## Assets

```{r, message=FALSE, echo=FALSE, warning=FALSE}
plotlist <- lapply(assetvars, plotvar, b = "dist_2_seg13", h=h0, df = df.hh, dist.exclude = "none", wide = TRUE)
plotlist

plotlist[[4]] +
  labs(x = "distance to border", y = "Loan Payments") +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/loans.png", sep = ""), width = 10, height = 7)

plotlist[[5]] +
  labs(x = "distance to border", y = "Net Inter Household Transfers") +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/totaltransfers.png", sep = ""), width = 10, height = 7)
```

## Shocks

```{r, message=FALSE, echo=FALSE, warning=FALSE}
plotlist <- lapply(shockvars, plotvar, b = "dist_2_seg13", h=h0, df = df.hh, dist.exclude = "none")
plotlist
```

## Coping

```{r, message=FALSE, echo=FALSE, warning=FALSE}
plotlist <- lapply(copingvars, plotvar, b = "dist_2_seg13", h=h0, df = df.hh, dist.exclude = "none")
plotlist

plotlist[[7]] +
  labs(x = "distance to border", y = "Migration") +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/migrants.png", sep = ""), width = 10, height = 7)
```

### regressions

First stage

```{r, warnings=FALSE}
rdstg1 <- lapply(aidvars, regout, b = "dist_2_seg13", df = df.hh, h = h0, b0 = b0, k = "triangular", vce = "hc1", 
                 dist.exclude = "none", wide = TRUE)

rdgazer(rdstg1, dvlabs = c("Received Aid", "Cumulative Aid"), 
        xlines = list(c("Wards", sapply(rdstg1, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdplacebo <- lapply(c(placebos[!(placebos %in% c("elevation", "shake_pga", "slope"))]), regout, b = "dist_2_seg13", df = df.hh, 
                    h = h0, b0 = b0, k = "triangular", vce = "hc1", dist.exclude = "none")
rdgazer(rdplacebo, dvlabs = str_replace_all(c(placebos[!(placebos %in% c("elevation", "shake_pga", "slope"))]), "_", " "), 
        xlines = list(c("Wards", sapply(rdplacebo, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdprice <- lapply(c(pricevars, infravars), regout, b = "dist_2_seg13", df = df.hh, 
                  h = h0, b0 = b0, k = "triangular", vce = "hc1", dist.exclude = "none", wide = TRUE)
rdgazer(rdprice, dvlabs = str_replace_all(c(pricevars, infravars), "_", " "), 
        xlines = list(c("Wards", sapply(rdprice, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")
```


```{r, message=FALSE, echo=FALSE, warning=FALSE}
rdnum1 <- lapply(numvars, regout, b = "dist_2_seg13", df = df.hh, h = h0, b0 = b0, fuzzy = TRUE, 
                 k = "triangular", vce = "hc1", dist.exclude = "none", wide = TRUE)
rdgazer(rdnum1, dvlabs = str_replace_all(numvars, "_", " "), 
        xlines = list(c("Wards", sapply(rdnum1, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))))
```


```{r, message=FALSE, echo=FALSE, warning=FALSE}
rdcash <- lapply(consumptionvars, regout, b = "dist_2_seg13", df = df.hh, h = h0, b0 = b0, fuzzy = TRUE, 
                 k = "triangular", vce = "hc1", dist.exclude = "none", wide = TRUE)
rdgazer(rdcash, dvlabs = str_replace_all(consumptionvars, "_", " "), 
        xlines = list(c("Wards", sapply(rdcash, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")
```

```{r, message=FALSE, echo=FALSE, warning=FALSE}
rdcash <- lapply(incomevars, regout, b = "dist_2_seg13", df = df.hh, h = h0, b0 = b0, fuzzy = TRUE, 
                 k = "triangular", vce = "hc1", dist.exclude = "none", wide = TRUE)
rdgazer(rdcash, dvlabs = str_replace_all(incomevars, "_", " "), 
        xlines = list(c("Wards", sapply(rdcash, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")
```

```{r, message=FALSE, echo=FALSE, warning=FALSE}
rdcash <- lapply(assetvars, regout, b = "dist_2_seg13", df = df.hh, h = h0, b0 = b0, fuzzy = TRUE, 
                 k = "triangular", vce = "hc1", dist.exclude = "none", wide = TRUE)
rdgazer(rdcash, dvlabs = str_replace_all(assetvars, "_", " "), 
        xlines = list(c("Wards", sapply(rdcash, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")
```


Wave 2 saw drought in some districts

```{r, message=FALSE, echo=FALSE, warning=FALSE}
rdshock <- lapply(shockvars, regout, b = "dist_2_seg13", df = df.hh, h = h0, b0 = b0, fuzzy = TRUE, 
                 k = "triangular", vce = "hc1", dist.exclude = "none", wide = TRUE)
rdgazer(rdshock, dvlabs = str_replace_all(shockvars, "_", " "), 
        xlines = list(c("Wards", sapply(rdshock, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")
```

### Probability of shock & coping vars

```{r, message=FALSE, echo=FALSE, warning=FALSE}
rdshock <- lapply(copingvars, regout, b = "dist_2_seg13", df = df.hh, h = h0, b0 = b0, fuzzy = TRUE, 
                 k = "triangular", vce = "hc1", dist.exclude = "none", wide = TRUE)
rdgazer(rdshock, dvlabs = str_replace_all(copingvars, "_", " "), 
        xlines = list(c("Wards", sapply(rdshock, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")
```

### Main Outcomes

```{r, warning=FALSE}
mainvars <- c("consumption", "food_consumption", "home_investment", "income_gross", "productive_assets", "total_outlays_net", "n_migrants")

rdmain <- lapply(mainvars, regout, b = "dist_2_seg13", df = df.hh, h = h0, b0 = b0, fuzzy = TRUE, 
                 k = "triangular", vce = "hc1", dist.exclude = "none", wide = TRUE)
rdgazer(rdmain, dvlabs = str_replace_all(mainvars, "_", " "), 
        xlines = list(c("Wards", sapply(rdmain, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")
```

Heterogeneity analysis
These are not exactly comparable to the rdrobust regressions which use diff standard errors and bias correction, but estimates are very close
land quintile control?

```{r}
df.int <- filter(df.hh, designation!="none", !is.na(age_hh), !is.na(class5)) %>%
  mutate(dist_pos = if_else(dist_2_seg13>0, dist_2_seg13, 0),
         dist_neg = if_else(dist_2_seg13<0, dist_2_seg13, 0),
         kwt = wt_hh*(1-abs(dist_2_seg13)/h0))

reg1 <- ivreg(food_consumption ~ aid_cumulative_bin + aid_cumulative_bin:gorkha_hh + dist_pos + dist_neg + shake_pga + as.factor(wave) + 
               as.factor(border_segment13) + dist_2_seg13:as.factor(border_segment13) +
                high_caste + class5 + poly(age_hh,2) + slope + elevation + gorkha_hh | 
          dist_14 + dist_14:gorkha_hh + dist_pos + dist_neg + shake_pga + as.factor(wave) + 
          as.factor(border_segment13) + dist_2_seg13:as.factor(border_segment13) + 
            high_caste + class5 + poly(age_hh,2) + slope + elevation + gorkha_hh,
      data = df.int, cluster = strata, weights = kwt, subset = abs(dist_2_seg13)<h0)

reg2 <- ivreg(food_consumption ~ aid_cumulative_bin + aid_cumulative_bin:as.factor(land_qtle) + dist_pos + dist_neg + shake_pga + as.factor(wave) + 
               as.factor(border_segment13) + dist_2_seg13:as.factor(border_segment13) +
                high_caste + class5 + poly(age_hh,2) + slope + elevation + gorkha_hh + as.factor(land_qtle) | 
          dist_14 + dist_14:as.factor(land_qtle) + dist_pos + dist_neg + shake_pga + as.factor(wave) + 
          as.factor(border_segment13) + dist_2_seg13:as.factor(border_segment13) + 
            high_caste + class5 + poly(age_hh,2) + slope + elevation + gorkha_hh + as.factor(land_qtle),
      data = df.int, cluster = strata, weights = kwt, subset = abs(dist_2_seg13)<h0)

reg3 <- ivreg(home_investment ~ aid_cumulative_bin + aid_cumulative_bin:gorkha_hh + dist_pos + dist_neg + shake_pga + as.factor(wave) + 
               as.factor(border_segment13) + dist_2_seg13:as.factor(border_segment13) +
                high_caste + class5 + poly(age_hh,2) + slope + elevation + gorkha_hh | 
          dist_14 + dist_14:gorkha_hh + dist_pos + dist_neg + shake_pga + as.factor(wave) + 
          as.factor(border_segment13) + dist_2_seg13:as.factor(border_segment13) + 
            high_caste + class5 + poly(age_hh,2) + slope + elevation + gorkha_hh,
      data = df.int, cluster = strata, weights = kwt, subset = abs(dist_2_seg13)<h0)

reg4 <- ivreg(home_investment ~ aid_cumulative_bin + aid_cumulative_bin:as.factor(land_qtle) + dist_pos + dist_neg + shake_pga + as.factor(wave) + 
               as.factor(border_segment13) + dist_2_seg13:as.factor(border_segment13) +
                high_caste + class5 + poly(age_hh,2) + slope + elevation + gorkha_hh + as.factor(land_qtle) | 
          dist_14 + dist_14:as.factor(land_qtle) + dist_pos + dist_neg + shake_pga + as.factor(wave) + 
          as.factor(border_segment13) + dist_2_seg13:as.factor(border_segment13) + 
            high_caste + class5 + poly(age_hh,2) + slope + elevation + gorkha_hh + as.factor(land_qtle),
      data = df.int, cluster = strata, weights = kwt, subset = abs(dist_2_seg13)<h0)


reg5 <- ivreg(total_outlays_net ~ aid_cumulative_bin + aid_cumulative_bin:gorkha_hh + dist_pos + dist_neg + shake_pga + as.factor(wave) + 
               as.factor(border_segment13) + dist_2_seg13:as.factor(border_segment13) +
                high_caste + class5 + poly(age_hh,2) + slope + elevation + gorkha_hh | 
          dist_14 + dist_14:gorkha_hh + dist_pos + dist_neg + shake_pga + as.factor(wave) + 
          as.factor(border_segment13) + dist_2_seg13:as.factor(border_segment13) + 
            high_caste + class5 + poly(age_hh,2) + slope + elevation + gorkha_hh,
      data = df.int, cluster = strata, weights = kwt, subset = abs(dist_2_seg13)<h0)

reg6 <- ivreg(total_outlays_net ~ aid_cumulative_bin + aid_cumulative_bin:as.factor(land_qtle) + dist_pos + dist_neg + shake_pga + as.factor(wave) + 
               as.factor(border_segment13) + dist_2_seg13:as.factor(border_segment13) +
                high_caste + class5 + poly(age_hh,2) + slope + elevation + gorkha_hh + as.factor(land_qtle) | 
          dist_14 + dist_14:as.factor(land_qtle) + dist_pos + dist_neg + shake_pga + as.factor(wave) + 
          as.factor(border_segment13) + dist_2_seg13:as.factor(border_segment13) + 
            high_caste + class5 + poly(age_hh,2) + slope + elevation + gorkha_hh + as.factor(land_qtle),
      data = df.int, cluster = strata, weights = kwt, subset = abs(dist_2_seg13)<h0)

stargazer(reg1, reg2, reg3, reg4, reg5, reg6, type = "text",
          omit.stat = "all", digits = 2, df = FALSE, 
          omit = c("Constant", "dist_pos", "dist_neg", "shake_pga", "wave", "border_segment13", "dist_2_seg13", 
                   "high_caste", "class5", "age_hh", "slope", "elevation"))
```

### Quantile RD

```{r, warning = FALSE}
cvarscutpts <- quantile(df.hh$consumption, seq(0,1,.1), na.rm = TRUE)
ctlist <- lapply(cvarscutpts, cutvars, var = "consumption", filter(df.hh, designation!="none"))
df <- cbind(filter(df.hh, designation!="none"), do.call(cbind, ctlist))

cvarst <- paste("t", cvarscutpts, sep = "")
cvarsu <- paste("u", cvarscutpts, sep = "")
cvarsc <- paste("c", cvarscutpts, sep = "")

rdc <- lapply(cvarst, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE, wide = TRUE)
rdgazer(rdc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcu <- lapply(cvarsu, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = "inv", wide = TRUE)
rdgazer(rdcu, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcu, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcc <- lapply(cvarsc, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE, wide = TRUE)
rdgazer(rdcc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

```


```{r}
b = boot(df, earthmovers, R = 1000, cutpts = cvarscutpts, parallel = "multicore")
b$t0
boot.ci(b, type = "perc")
```

```{r, warning=FALSE}
qplot("consumption", filter(df.hh, designation!="none"), grid = cvarscutpts[2:10], wide = TRUE) +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/qplot_consumption.png", sep = ""), width = 10, height = 7)
```


Food Consumption - 100,000 is about $2.7/day, close to the median

```{r, warning = FALSE}
cvarscutpts <- quantile(df.hh$food_consumption, seq(0, 1, .1), na.rm = TRUE)
ctlist <- lapply(cvarscutpts, cutvars, var = "food_consumption", filter(df.hh, designation!="none"))
df <- cbind(filter(df.hh, designation!="none"), do.call(cbind, ctlist))

cvarst <- paste("t", cvarscutpts, sep = "")
cvarsu <- paste("u", cvarscutpts, sep = "")
cvarsc <- paste("c", cvarscutpts, sep = "")

rdc <- lapply(cvarst, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE, wide = TRUE)
rdgazer(rdc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcu <- lapply(cvarsu, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = "inv", wide = TRUE)
rdgazer(rdcu, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcu, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcc <- lapply(cvarsc, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE, wide = TRUE)
rdgazer(rdcc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

foodt <- unlist(lapply(rdc, function(x) x$Estimate[1]))
foodu <- unlist(lapply(rdcu, function(x) x$Estimate[1]))
foodRD <- list(foodt, foodu, cvarscutpts)
saveRDS(foodRD, paste(rootdir, "/data/model_output/foodRD.rds", sep = ""))
```

```{r}
b = boot(df, earthmovers, R = 1000, cutpts = cvarscutpts, weights = df$wt_hh, strata = df$strata, 
         parallel = "multicore", ncpus = detectCores() - 2)
b$t0
boot.ci(b, type = "perc", conf = c(.9, .95, .99))
```


```{r, warning=FALSE}
q1 <- qplot("food_consumption", filter(df.hh, designation!="none"), grid = cvarscutpts[2:10], wide = TRUE) +
  theme(text = element_text(size = 20)) + labs(x = "Food Consumption", y = "P(X<x)", color = "Aid")
q1
ggsave(paste(rootdir, "/presentation_materials/qplot_food.png", sep = ""), width = 10, height = 7)
```


```{r, warning = FALSE}
cvarscutpts <- quantile(df.hh$income_gross, seq(0,1,.1), na.rm = TRUE)
ctlist <- lapply(cvarscutpts, cutvars, var = "income_gross", filter(df.hh, designation!="none"))
df <- cbind(filter(df.hh, designation!="none"), do.call(cbind, ctlist))

cvarst <- paste("t", cvarscutpts, sep = "")
cvarsu <- paste("u", cvarscutpts, sep = "")
cvarsc <- paste("c", cvarscutpts, sep = "")

rdc <- lapply(cvarst, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE, wide = TRUE)
rdgazer(rdc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcu <- lapply(cvarsu, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = "inv", wide = TRUE)
rdgazer(rdcu, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcu, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcc <- lapply(cvarsc, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE, wide = TRUE)
rdgazer(rdcc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")
```


```{r}
b = boot(df, earthmovers, R = 1000, cutpts = cvarscutpts, weights = df$wt_hh, strata = df$strata, 
         parallel = "multicore", ncpus = detectCores() - 2)
b$t0
boot.ci(b, type = "perc", conf = c(.9, .95, .99))
```


```{r, warning = FALSE}
q2 <- qplot("income_gross", filter(df.hh, designation!="none"), grid = cvarscutpts[2:10], wide = TRUE) +
  theme(text = element_text(size = 20)) + labs(x = "Income", y = "P(X<x)")
q2
ggsave(paste(rootdir, "/presentation_materials/qplot_income.png", sep = ""), width = 10, height = 7)
```

```{r, warning = FALSE}
cvarscutpts <- quantile(df.hh$productive_assets, seq(0,1,.1), na.rm = TRUE)
ctlist <- lapply(cvarscutpts, cutvars, var = "productive_assets", filter(df.hh, designation!="none"))
df <- cbind(filter(df.hh, designation!="none"), do.call(cbind, ctlist))

cvarst <- paste("t", cvarscutpts, sep = "")
cvarsu <- paste("u", cvarscutpts, sep = "")
cvarsc <- paste("c", cvarscutpts, sep = "")

rdc <- lapply(cvarst, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE, wide = TRUE)
rdgazer(rdc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcu <- lapply(cvarsu, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = "inv", wide = TRUE)
rdgazer(rdcu, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcu, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcc <- lapply(cvarsc, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE, wide = TRUE)
rdgazer(rdcc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")
```

```{r}
b = boot(df, earthmovers, R = 1000, cutpts = cvarscutpts, weights = df$wt_hh, strata = df$strata, 
         parallel = "multicore", ncpus = detectCores() - 2)
b$t0
boot.ci(b, type = "perc", conf = c(.9, .95, .99)) 
```

```{r, warning = FALSE}
qplot("productive_assets", filter(df.hh, designation!="none"), grid = cvarscutpts[2:10], wide = TRUE) +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/qplot_assets.png", sep = ""), width = 10, height = 7)
```

```{r, warning = FALSE}
cvarscutpts <- quantile(df.hh$home_investment, c(0, .9, .95, .99), na.rm = TRUE)
ctlist <- lapply(cvarscutpts, cutvars, var = "home_investment", filter(df.hh, designation!="none"))
df <- cbind(filter(df.hh, designation!="none"), do.call(cbind, ctlist))

cvarst <- paste("t", cvarscutpts, sep = "")
cvarsu <- paste("u", cvarscutpts, sep = "")
cvarsc <- paste("c", cvarscutpts, sep = "")

rdc <- lapply(cvarst, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE, wide = TRUE)
rdgazer(rdc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcu <- lapply(cvarsu, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = "inv", wide = TRUE)
rdgazer(rdcu, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcu, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcc <- lapply(cvarsc, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE, wide = TRUE)
rdgazer(rdcc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

homet <- unlist(lapply(rdc, function(x) x$Estimate[1]))
homeu <- unlist(lapply(rdcu, function(x) x$Estimate[1]))
homeRD <- list(homet, homeu, cvarscutpts)
saveRDS(homeRD, paste(rootdir, "/data/model_output/homeRD.rds", sep = ""))
```

```{r}
b = boot(df, earthmovers, R = 1000, cutpts = cvarscutpts, weights = df$wt_hh, strata = df$strata, 
         parallel = "multicore", ncpus = detectCores() - 2)
b$t0
boot.ci(b, type = "perc", conf = c(.9, .95, .99))
```

```{r, warning = FALSE}
q3 <- qplot("home_investment", filter(df.hh, designation!="none"), grid = cvarscutpts, wide = TRUE) +
  theme(text = element_text(size = 20)) + labs(x = "Housing Investment", y = "P(X<x)", color = "Aid")
q3
ggsave(paste(rootdir, "/presentation_materials/qplot_investment.png", sep = ""), width = 10, height = 7)
```

```{r, warning = FALSE}
cvarscutpts <- unique(quantile(df.hh$total_outlays_net, seq(0,1,.1), na.rm = TRUE))
ctlist <- lapply(cvarscutpts, cutvars, var = "total_outlays_net", filter(df.hh, designation!="none"))
df <- cbind(filter(df.hh, designation!="none"), do.call(cbind, ctlist))

cvarst <- paste("t", cvarscutpts, sep = "")
cvarsu <- paste("u", cvarscutpts, sep = "")
cvarsc <- paste("c", cvarscutpts, sep = "")

rdc <- lapply(cvarst, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE, wide = TRUE)
rdgazer(rdc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcu <- lapply(cvarsu, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = "inv", wide = TRUE)
rdgazer(rdcu, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcu, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcc <- lapply(cvarsc, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE, wide = TRUE)
rdgazer(rdcc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

loant <- unlist(lapply(rdc, function(x) x$Estimate[1]))
loanu <- unlist(lapply(rdcu, function(x) x$Estimate[1]))
loanRD <- list(loant, loanu, cvarscutpts)
saveRDS(loanRD, paste(rootdir, "/data/model_output/loanRD.rds", sep = ""))
```

```{r}
b = boot(df, earthmovers, R = 1000, cutpts = cvarscutpts, weights = df$wt_hh, strata = df$strata, 
         parallel = "multicore", ncpus = detectCores() - 2)
b$t0
boot.ci(b, type = "perc", conf = c(.9, .95, .99))
```


```{r, warning = FALSE}
q4 <- qplot("total_outlays_net", filter(df.hh, designation!="none"), grid = cvarscutpts[2:10], wide = TRUE) +
  theme(text = element_text(size = 20)) + labs(x = "Inter-Household Transfers", y = "P(X<x)")
q4
ggsave(paste(rootdir, "/presentation_materials/qplot_transfers.png", sep = ""), width = 10, height = 7)
```


```{r}
cowplot::plot_grid(q1+guides(color = "none"), q2+guides(color = "none"), q3+guides(color = "none"), q4+guides(color = "none"), nrow = 2)
ggsave(paste(rootdir, "/presentation_materials/qplot4.png", sep = ""), width = 10, height = 7)

cowplot::plot_grid(q3+guides(color = "none"), q4 + labs(color = "Aid"), rel_widths = c(3,4))
ggsave(paste(rootdir, "/presentation_materials/qplot2.png", sep = ""), width = 14, height = 7)

cowplot::plot_grid(q1+guides(color = "none"), q3+guides(color = "none"), q4+labs(color = "Aid"), nrow = 1, rel_widths = c(2,2,3))
ggsave(paste(rootdir, "/presentation_materials/qplot3.png", sep = ""), width = 14, height = 7)
```

```{r}
q1 + 
  geom_segment(aes(x = foodRD[[3]][5], xend = foodRD[[3]][5], y = foodRD[[1]][5], yend = foodRD[[2]][5]), color = "red", size = 2) + 
  labs(x = "Food Consumption", y = "P(X<x)", color = "Aid")
ggsave(paste(rootdir, "/presentation_materials/qplot_food_1bar.png", sep = ""), width = 10, height = 7)

q1 + 
  geom_segment(aes(x = foodRD[[3]][5], xend = foodRD[[3]][5], y = foodRD[[1]][5], yend = foodRD[[2]][5]), color = "red", size = 2) + 
  geom_segment(aes(x = foodRD[[3]][9], xend = foodRD[[3]][9], y = foodRD[[1]][9], yend = foodRD[[2]][9]), color = "red", size = 2) + 
  labs(x = "Food Consumption", y = "P(X<x)", color = "Aid")
ggsave(paste(rootdir, "/presentation_materials/qplot_food_2bar.png", sep = ""), width = 10, height = 7)
  
q3 + 
  geom_segment(aes(x = 0, xend = 0, y = homeRD[[1]][1], yend = homeRD[[2]][1]), color = "red", size = 2) + 
  labs(x = "Housing Investment", y = "P(X<x)", color = "Aid")
ggsave(paste(rootdir, "/presentation_materials/qplot_investment_1bar.png", sep = ""), width = 10, height = 7)

q3 + 
  geom_segment(aes(x = 0, xend = 0, y = homeRD[[1]][1], yend = homeRD[[2]][1]), color = "red", size = 2) + 
  geom_segment(aes(x = homeRD[[3]][2], xend = homeRD[[3]][2], y = homeRD[[1]][2], yend = homeRD[[2]][2]), color = "red", size = 2) + 
  labs(x = "Housing Investment", y = "P(X<x)", color = "Aid")
ggsave(paste(rootdir, "/presentation_materials/qplot_investment_2bar.png", sep = ""), width = 10, height = 7)

q3 + 
  geom_segment(aes(x = homeRD[[3]][2], xend = homeRD[[3]][2], y = homeRD[[1]][2], yend = homeRD[[2]][2]), color = "red", size = 2) + 
  geom_segment(aes(x = 0, xend = 0, y = homeRD[[1]][1], yend = homeRD[[2]][1]), color = "red", size = 2) + 
  geom_segment(aes(x = homeRD[[3]][3], xend = homeRD[[3]][3], y = homeRD[[1]][3], yend = homeRD[[2]][3]), color = "red", size = 2) + 
  labs(x = "Housing Investment", y = "P(X<x)", color = "Aid")
ggsave(paste(rootdir, "/presentation_materials/qplot_investment_3bar.png", sep = ""), width = 10, height = 7)
```


