---
title: "WB HRVS estimation"
author: "Matthew Gordon"
date: "7/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
rootdir <- dirname(getwd())
```

### Load packages and data

```{r, message=FALSE, echo=FALSE, warning=FALSE}
library(tidyverse)
library(sf)
library(lfe)
library(AER)
library(ggnewscale)
library(cowplot)
library(stargazer)
library(sandwich)
library(readstata13)
#devtools::install_github("mdgordo/rdrobust",ref="master")
library(rdrobust)
#devtools::install_github("mdgordo/dumbells",ref="master")
library(dumbells)
library(rdpower)
library(boot)
library(parallel)
source(paste(rootdir, "/code/rdhelpers.r", sep = ""))

df.hh <- read_csv(paste(rootdir, "/data/processed/full_panel.csv", sep = ""), guess_max = 7500)
df.hh <- filter(df.hh, !is.na(income_gross) & income_gross>0 & food_consumption>0)
```

Define vars

```{r}
placebos <- c("elevation", "shake_pga", "gorkha_hh", "gorkha_loss_ever", "high_caste", "age_hh", "highest_ed", 
              "always_lived_house", "always_lived_dist", "slope", "pub_transfers", "NGO_transfers")
infravars <- c("time_to_bank", "time_to_school", "time_to_health")
aidvars <- c("aid_cumulative_bin", "aid_cumulative")
numvars <- c("currentlyliving", "under5", "under18", "over65", "femalehh", "extended_members", "children_attending")
consumptionvars <- c("food_consumption", "durables_consumption", "home_investment", "transportation", "energy_utilities", "ceremonial_expenses", "other_consumption")
incomevars <- c("remittance_income", "annual_wages", "ag_livestock_income", "pub_transfers", "inputs")
percapitavars <- c("income_pc", "consumption_pc", "food_consumption_pc")
pricevars <- c("chicken_price", "rice_price", "lentil_price", "sugar_price", "mutton_price", "potato_price")
assetvars <- c("livestock_sales", "livestock_purchases", "loans_taken_past_year", "loan_payments", "total_outlays_net")
shockvars <- c("natural_shocks", "market_shocks", "idiosyncratic_shocks")
copingvars <- c("dissaving", "felt_hunger", "school_interrupt", 
                "child_labor", "child_days_worked", "child_wage_days", "n_migrants")
```

#### Regression Discontinuity

### MSE bandwidths - Cattaneo paper
Can try also with aid_total - similar

```{r, warning=FALSE}
bws <- rbind(optbw("aid_cumulative_bin", b = "dist_2_seg13", df = df.hh, dist.exclude = "none"),
      optbw("consumption", b = "dist_2_seg13", df = df.hh, fuzzy = TRUE, dist.exclude = "none"))

h0 <- bws[2,1]
b0 <- bws[2,3]
```

Power calculations

```{r, warning = FALSE}
df.pow <- filter(df.hh, !is.na(consumption) & designation!="none")
powcovs <- model.matrix(~as.factor(df.pow$border_segment13)+as.factor(df.pow$border_segment13)*df.pow$dist_2_seg13 + df.pow$shake_pga + as.factor(df.pow$wave))
powcovs <- powcovs[, !(colnames(powcovs) %in% c("(Intercept)", "df.pow$dist_2_seg13"))]

df.pow <- mutate(df.pow, fcs60 = if_else(consumption < 60000, 1, 0),
                fcs100 = if_else(consumption < 100000, 1, 0),
                fcs200up = if_else(consumption < 200000, 0, 1))

print("First Stage")
a <- rdpower(data = cbind(df.pow$aid_cumulative_bin, df.pow$dist_2_seg13), h = h0, b = b0, kernel = "triangular", vce = "hc1", 
        covs =  powcovs, cluster = df.pow$strata, weights = df.pow$wt_hh, tau = .27)
print("Consumption")
a <- rdpower(data = cbind(df.pow$consumption, df.pow$dist_2_seg13), h = h0, b = b0, kernel = "triangular", vce = "hc1", 
        covs =  powcovs, cluster = df.pow$strata, weights = df.pow$wt_hh)
print("Consumption w IV")
a <- rdpower(data = cbind(df.pow$consumption, df.pow$dist_2_seg13), h = h0, b = b0, kernel = "triangular", vce = "hc1", 
        covs =  powcovs, cluster = df.pow$strata, weights = df.pow$wt_hh, fuzzy = df.pow$aid_cumulative_bin)
print("Consumption Dummies")
a <- rdpower(data = cbind(df.pow$fcs60, df.pow$dist_2_seg13), h = h0, b = b0, kernel = "triangular", vce = "hc1", 
        covs =  powcovs, cluster = df.pow$strata, weights = df.pow$wt_hh, fuzzy = df.pow$aid_cumulative_bin)

a <- rdpower(data = cbind(df.pow$fcs100, df.pow$dist_2_seg13), h = h0, b = b0, kernel = "triangular", vce = "hc1", 
        covs =  powcovs, cluster = df.pow$strata, weights = df.pow$wt_hh, fuzzy = df.pow$aid_cumulative_bin)

a <- rdpower(data = cbind(df.pow$fcs200up, df.pow$dist_2_seg13), h = h0, b = b0, kernel = "triangular", vce = "hc1", 
        covs =  powcovs, cluster = df.pow$strata, weights = df.pow$wt_hh, fuzzy = df.pow$aid_cumulative_bin)
```

### Functions for Mccrary test
Discrete version based on: https://cattaneo.princeton.edu/aie-rdd/Frandsen_2016_AIE.pdf
Sampling frame based on 2010 census - need to adjust to hhs per unit area

```{r}
mcplot <- histfunc("dist_2_seg13", filter(df.hh, wave==1), h = h0, dist.exclude = "none")

mcplot + labs(x = "distance to border") + theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/mccrary.png", sep = ""), width = 10, height = 7)
```

### RD plots

### Aid vars

```{r, message=FALSE, warning=FALSE}
plotlist <- lapply(aidvars, plotvar, b = "dist_2_seg13", h=h0, df = df.hh, dist.exclude = "none")
plotlist

p2 = plotlist[[1]] +
  labs(x = "distance to border", y = "residualized fraction receiving aid") +
  theme(text = element_text(size = 20)) + ylim(-.5,.5)
p2
ggsave(paste(rootdir, "/presentation_materials/aid_bin.png", sep = ""), width = 10, height = 7) 

plotlist[[2]] +
  labs(x = "distance to border", y = "Amount Received") +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/aid_amt.png", sep = ""), width = 10, height = 7) 

```

### Placebo tests

```{r, message=FALSE, warning=FALSE}
plotlist <- lapply(placebos[!placebos %in% c("elevation", "shake_pga")], plotvar, b = "dist_2_seg13", h=h0, df = df.hh, dist.exclude = "none")
plotlist
p1 = plotlist[[2]] +
  labs(x = "distance to border", y = "residualized reported earthquake losses") +
  theme(text = element_text(size = 20))
p1
ggsave(paste(rootdir, "/presentation_materials/losses_placebo.png", sep = ""), width = 10, height = 7)

plotlist[[10]] +
  labs(x = "distance to border", y = "residualized NGO aid") +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/NGO_placebo.png", sep = ""), width = 10, height = 7)


cowplot::plot_grid(p2, p1)
ggsave(paste(rootdir, "/presentation_materials/aidanddamage.png", sep = ""), width = 13, height = 7) 
```

```{r, message=FALSE, warning=FALSE}
lapply(infravars, plotvar, b = "dist_2_seg13", h=h0, df = df.hh, dist.exclude = "none")
lapply(pricevars, plotvar, b = "dist_2_seg13", h=h0, df = df.hh, dist.exclude = "none")
```


## HH Composition

```{r}
plotlist <- lapply(numvars, plotvar, b = "dist_2_seg13", h=h0, df = df.hh, dist.exclude = "none")
plotlist

plotlist[[1]] +
  labs(x = "distance to border", y = "Currently Living in HH") +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/currentlyliving.png", sep = ""), width = 10, height = 7)

plotlist[[5]] +
  labs(x = "distance to border", y = "Female Headed Household") +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/FHH.png", sep = ""), width = 10, height = 7)

```

## Consumption

```{r}
plotlist <- lapply(consumptionvars, plotvar, b = "dist_2_seg13", h=h0, df = df.hh, ihs=FALSE, dist.exclude = "none")
plotlist

plotlist[[1]] +
  labs(x = "distance to border", y = "Food Consumption") +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/food.png", sep = ""), width = 10, height = 7)
```

## Income

```{r, message=FALSE, echo=FALSE, warning=FALSE}
plotlist <- lapply(incomevars, plotvar, b = "dist_2_seg13", h=h0, df = df.hh, ihs=FALSE, dist.exclude = "none")
plotlist

plotlist[[1]] +
  labs(x = "distance to border", y = "Remittances") +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/remittances.png", sep = ""), width = 10, height = 7)
incomevars
```

## Assets

```{r, message=FALSE, echo=FALSE, warning=FALSE}
plotlist <- lapply(assetvars, plotvar, b = "dist_2_seg13", h=h0, df = df.hh, dist.exclude = "none")
plotlist

plotlist[[4]] +
  labs(x = "distance to border", y = "Loan Payments") +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/loans.png", sep = ""), width = 10, height = 7)

plotlist[[5]] +
  labs(x = "distance to border", y = "Net Inter Household Transfers") +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/totaltransfers.png", sep = ""), width = 10, height = 7)
```

## Shocks

```{r, message=FALSE, echo=FALSE, warning=FALSE}
plotlist <- lapply(shockvars, plotvar, b = "dist_2_seg13", h=h0, df = df.hh, dist.exclude = "none")
plotlist
```

## Coping

```{r, message=FALSE, echo=FALSE, warning=FALSE}
plotlist <- lapply(copingvars, plotvar, b = "dist_2_seg13", h=h0, df = df.hh, dist.exclude = "none")
plotlist

plotlist[[7]] +
  labs(x = "distance to border", y = "Migration") +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/migrants.png", sep = ""), width = 10, height = 7)
```

### regressions

First stage

```{r, warnings=FALSE}
rdstg1 <- lapply(aidvars, regout, b = "dist_2_seg13", df = df.hh, h = h0, b0 = b0, k = "triangular", vce = "hc1", dist.exclude = "none")

rdgazer(rdstg1, dvlabs = c("Received Aid", "Cumulative Aid"), 
        xlines = list(c("Wards", sapply(rdstg1, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "latex")

rdplacebo <- lapply(c(placebos[!(placebos %in% c("elevation", "shake_pga", "slope"))]), regout, b = "dist_2_seg13", df = df.hh, 
                    h = h0, b0 = b0, k = "triangular", vce = "hc1", dist.exclude = "none")
rdgazer(rdplacebo, dvlabs = str_replace_all(c(placebos[!(placebos %in% c("elevation", "shake_pga", "slope"))]), "_", " "), 
        xlines = list(c("Wards", sapply(rdplacebo, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "latex")

rdprice <- lapply(c(pricevars, infravars), regout, b = "dist_2_seg13", df = df.hh, 
                  h = h0, b0 = b0, k = "triangular", vce = "hc1", dist.exclude = "none")
rdgazer(rdprice, dvlabs = str_replace_all(c(pricevars, infravars), "_", " "), 
        xlines = list(c("Wards", sapply(rdprice, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "latex")
```


```{r, message=FALSE, echo=FALSE, warning=FALSE}
rdnum1 <- lapply(numvars, regout, b = "dist_2_seg13", df = df.hh, h = h0, b0 = b0, fuzzy = TRUE, 
                 k = "triangular", vce = "hc1", dist.exclude = "none")
rdgazer(rdnum1, dvlabs = str_replace_all(numvars, "_", " "), 
        xlines = list(c("Wards", sapply(rdnum1, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))))
```


```{r, message=FALSE, echo=FALSE, warning=FALSE}
rdcash <- lapply(consumptionvars, regout, b = "dist_2_seg13", df = df.hh, h = h0, b0 = b0, fuzzy = TRUE, 
                 k = "triangular", vce = "hc1", dist.exclude = "none")
rdgazer(rdcash, dvlabs = str_replace_all(consumptionvars, "_", " "), 
        xlines = list(c("Wards", sapply(rdcash, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")
```

```{r, message=FALSE, echo=FALSE, warning=FALSE}
rdcash <- lapply(incomevars, regout, b = "dist_2_seg13", df = df.hh, h = h0, b0 = b0, fuzzy = TRUE, 
                 k = "triangular", vce = "hc1", dist.exclude = "none")
rdgazer(rdcash, dvlabs = str_replace_all(incomevars, "_", " "), 
        xlines = list(c("Wards", sapply(rdcash, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")
```

```{r, message=FALSE, echo=FALSE, warning=FALSE}
rdcash <- lapply(assetvars, regout, b = "dist_2_seg13", df = df.hh, h = h0, b0 = b0, fuzzy = TRUE, 
                 k = "triangular", vce = "hc1", dist.exclude = "none")
rdgazer(rdcash, dvlabs = str_replace_all(assetvars, "_", " "), 
        xlines = list(c("Wards", sapply(rdcash, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")
```


Wave 2 saw drought in some districts

```{r, message=FALSE, echo=FALSE, warning=FALSE}
rdshock <- lapply(shockvars, regout, b = "dist_2_seg13", df = df.hh, h = h0, b0 = b0, fuzzy = TRUE, 
                 k = "triangular", vce = "hc1", dist.exclude = "none")
rdgazer(rdshock, dvlabs = str_replace_all(shockvars, "_", " "), 
        xlines = list(c("Wards", sapply(rdshock, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")
```

### Probability of shock & coping vars

```{r, message=FALSE, echo=FALSE, warning=FALSE}
rdshock <- lapply(copingvars, regout, b = "dist_2_seg13", df = df.hh, h = h0, b0 = b0, fuzzy = TRUE, 
                 k = "triangular", vce = "hc1", dist.exclude = "none")
rdgazer(rdshock, dvlabs = str_replace_all(copingvars, "_", " "), 
        xlines = list(c("Wards", sapply(rdshock, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")
```

### Main Outcomes

```{r, warning=FALSE}
mainvars <- c("consumption", "food_consumption", "home_investment", "income_gross", "productive_assets", "total_outlays_net", "n_migrants")

rdmain <- lapply(mainvars, regout, b = "dist_2_seg13", df = df.hh, h = h0, b0 = b0, fuzzy = TRUE, 
                 k = "triangular", vce = "hc1", dist.exclude = "none")
rdgazer(rdmain, dvlabs = str_replace_all(mainvars, "_", " "), 
        xlines = list(c("Wards", sapply(rdmain, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "latex")
```

Effect on consumption smoothing

```{r}
df.hh$vdc_dist <- paste(df.hh$vdc, df.hh$district, sep = "_")
vdclist <- data.frame("vdc" = unique(df.hh$vdc_dist))

townsenderator <- function(i){
  df <- filter(df.hh, vdc_dist==i, food_consumption > 0, income_gross > 0)
  mod <- felm(log(food_consumption) ~ log(income_gross) | as.factor(hhid),
              data = df, weights = df$wt_hh, na.action = na.omit)
  return(mod$coefficients[1,1])
}

vdclist$betaT = unlist(lapply(vdclist$vdc, townsenderator))

df <- merge(df.hh, vdclist, by.x = "vdc_dist", by.y = "vdc") %>%
  filter(designation != "none", wave==1)

covs <- model.matrix(~as.factor(df$border_segment13)+as.factor(df$border_segment13)*df$dist_2_seg13 + df$shake_pga)
covs <- covs[, !(colnames(covs) %in% c("(Intercept)", "df$dist_2_seg13"))]
resreg <- lm(df$betaT ~ covs)
df$resreg <- resreg$residuals

out <- rdrobust(y = df$betaT, x = df$dist_2_seg13, c = 0, fuzzy = df$received_aid, 
                weights = df$wt_hh, cluster = df$strata, kernel = "triangular", vce = "hc1", covs = covs)
summary(out)

df <- filter(df, abs(dist_2_seg13)<b0)
r <- rdplot(y = df$resreg, x = df$dist_2_seg13, c = 0, weights = df$wt_hh, binselect = "qsmv", kernel = "triangular", 
              poly = TRUE, title = NULL, y.label = "Coefficient of Consumption Smoothing", x.label = "Distance to Border", hide = TRUE, p = 1)
r$rdplot
```


### Quantile RD

```{r, warning = FALSE}
cvarscutpts <- quantile(df.hh$consumption, seq(0,1,.1), na.rm = TRUE)
ctlist <- lapply(cvarscutpts, cutvars, var = "consumption", filter(df.hh, designation!="none"))
df <- cbind(filter(df.hh, designation!="none"), do.call(cbind, ctlist))

cvarst <- paste("t", cvarscutpts, sep = "")
cvarsu <- paste("u", cvarscutpts, sep = "")
cvarsc <- paste("c", cvarscutpts, sep = "")

rdc <- lapply(cvarst, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE)
rdgazer(rdc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcu <- lapply(cvarsu, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = "inv")
rdgazer(rdcu, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcu, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcc <- lapply(cvarsc, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE)
rdgazer(rdcc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

b = boot(df, earthmovers, R = 1000, cutpts = cvarscutpts, parallel = "multicore")
b$t0
boot.ci(b, type = "perc")
```

```{r, warning=FALSE}
qplot("consumption", filter(df.hh, designation!="none")) +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/qplot_consumption.png", sep = ""), width = 10, height = 7)
```


Food Consumption - 100,000 is about $2.7/day, close to the median

```{r, warning = FALSE}
cvarscutpts <- quantile(df.hh$food_consumption, seq(0, 1, .1))
ctlist <- lapply(cvarscutpts, cutvars, var = "food_consumption", filter(df.hh, designation!="none"))
df <- cbind(filter(df.hh, designation!="none"), do.call(cbind, ctlist))

cvarst <- paste("t", cvarscutpts, sep = "")
cvarsu <- paste("u", cvarscutpts, sep = "")
cvarsc <- paste("c", cvarscutpts, sep = "")

rdc <- lapply(cvarst, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE)
rdgazer(rdc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcu <- lapply(cvarsu, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = "inv")
rdgazer(rdcu, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcu, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcc <- lapply(cvarsc, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE)
rdgazer(rdcc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

b = boot(df, earthmovers, R = 1000, cutpts = cvarscutpts, weights = df$wt_hh, strata = df$strata, 
         parallel = "multicore", ncpus = detectCores() - 2)
b$t0
boot.ci(b, type = "perc", conf = c(.9, .95, .99))
```


```{r, warning=FALSE}
q1 <- qplot("food_consumption", filter(df.hh, designation!="none")) +
  theme(text = element_text(size = 20)) + labs(x = "Food Consumption", y = "P(X<x)")
q1
ggsave(paste(rootdir, "/presentation_materials/qplot_food.png", sep = ""), width = 10, height = 7)
```


```{r, warning = FALSE}
cvarscutpts <- quantile(df.hh$income_gross, seq(0,1,.1), na.rm = TRUE)
ctlist <- lapply(cvarscutpts, cutvars, var = "income_gross", filter(df.hh, designation!="none"))
df <- cbind(filter(df.hh, designation!="none"), do.call(cbind, ctlist))

cvarst <- paste("t", cvarscutpts, sep = "")
cvarsu <- paste("u", cvarscutpts, sep = "")
cvarsc <- paste("c", cvarscutpts, sep = "")

rdc <- lapply(cvarst, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE)
rdgazer(rdc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "latex")

rdcu <- lapply(cvarsu, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = "inv")
rdgazer(rdcu, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcu, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "latex")

rdcc <- lapply(cvarsc, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE)
rdgazer(rdcc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

b = boot(df, earthmovers, R = 1000, cutpts = cvarscutpts, weights = df$wt_hh, strata = df$strata, 
         parallel = "multicore", ncpus = detectCores() - 2)
b$t0
boot.ci(b, type = "perc", conf = c(.9, .95, .99))
```


```{r, warning = FALSE}
q2 <- qplot("income_gross", filter(df.hh, designation!="none")) +
  theme(text = element_text(size = 20)) + labs(x = "Income", y = "P(X<x)")
q2
ggsave(paste(rootdir, "/presentation_materials/qplot_income.png", sep = ""), width = 10, height = 7)
```

```{r, warning = FALSE}
cvarscutpts <- quantile(df.hh$productive_assets, seq(0,1,.1), na.rm = TRUE)
ctlist <- lapply(cvarscutpts, cutvars, var = "productive_assets", filter(df.hh, designation!="none"))
df <- cbind(filter(df.hh, designation!="none"), do.call(cbind, ctlist))

cvarst <- paste("t", cvarscutpts, sep = "")
cvarsu <- paste("u", cvarscutpts, sep = "")
cvarsc <- paste("c", cvarscutpts, sep = "")

rdc <- lapply(cvarst, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE)
rdgazer(rdc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcu <- lapply(cvarsu, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = "inv")
rdgazer(rdcu, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcu, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcc <- lapply(cvarsc, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE)
rdgazer(rdcc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

b = boot(df, earthmovers, R = 1000, cutpts = cvarscutpts, weights = df$wt_hh, strata = df$strata, 
         parallel = "multicore", ncpus = detectCores() - 2)
b$t0
boot.ci(b, type = "perc", conf = c(.9, .95, .99)) 
```

```{r, warning = FALSE}
qplot("productive_assets", filter(df.hh, designation!="none")) +
  theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/qplot_assets.png", sep = ""), width = 10, height = 7)
```

```{r, warning = FALSE}
cvarscutpts <- quantile(df.hh$home_investment, c(0, .9, .95, .99), na.rm = TRUE)
ctlist <- lapply(cvarscutpts, cutvars, var = "home_investment", filter(df.hh, designation!="none"))
df <- cbind(filter(df.hh, designation!="none"), do.call(cbind, ctlist))

cvarst <- paste("t", cvarscutpts, sep = "")
cvarsu <- paste("u", cvarscutpts, sep = "")
cvarsc <- paste("c", cvarscutpts, sep = "")

rdc <- lapply(cvarst, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE)
rdgazer(rdc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcu <- lapply(cvarsu, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = "inv")
rdgazer(rdcu, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcu, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcc <- lapply(cvarsc, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE)
rdgazer(rdcc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

b = boot(df, earthmovers, R = 1000, cutpts = cvarscutpts, weights = df$wt_hh, strata = df$strata, 
         parallel = "multicore", ncpus = detectCores() - 2)
b$t0
boot.ci(b, type = "perc", conf = c(.9, .95, .99))
```

```{r, warning = FALSE}
q3 <- qplot("home_investment", filter(df.hh, designation!="none"), grid = c(0, 100000, 250000, 500000)) +
  theme(text = element_text(size = 20)) + labs(x = "Housing Investment", y = "P(X<x)")
q3
ggsave(paste(rootdir, "/presentation_materials/qplot_investment.png", sep = ""), width = 10, height = 7)
```

```{r, warning = FALSE}
cvarscutpts <- unique(quantile(df.hh$total_outlays_net, seq(0,1,.1), na.rm = TRUE))
ctlist <- lapply(cvarscutpts, cutvars, var = "total_outlays_net", filter(df.hh, designation!="none"))
df <- cbind(filter(df.hh, designation!="none"), do.call(cbind, ctlist))

cvarst <- paste("t", cvarscutpts, sep = "")
cvarsu <- paste("u", cvarscutpts, sep = "")
cvarsc <- paste("c", cvarscutpts, sep = "")

rdc <- lapply(cvarst, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE)
rdgazer(rdc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcu <- lapply(cvarsu, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = "inv")
rdgazer(rdcu, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcu, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcc <- lapply(cvarsc, regout, b = "dist_2_seg13", df = df, h = h0, b0 = b0, k = "triangular", vce = "hc1", fuzzy = TRUE)
rdgazer(rdcc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

b = boot(df, earthmovers, R = 1000, cutpts = cvarscutpts, weights = df$wt_hh, strata = df$strata, 
         parallel = "multicore", ncpus = detectCores() - 2)
b$t0
boot.ci(b, type = "perc", conf = c(.9, .95, .99))
```


```{r, warning = FALSE}
q4 <- qplot("total_outlays_net", filter(df.hh, designation!="none")) +
  theme(text = element_text(size = 20)) + labs(x = "Inter-Household Transfers", y = "P(X<x)")
q4
ggsave(paste(rootdir, "/presentation_materials/qplot_transfers.png", sep = ""), width = 10, height = 7)
```


```{r}
cowplot::plot_grid(q1, q2, q3, q4, nrow = 2)
ggsave(paste(rootdir, "/presentation_materials/qplot4.png", sep = ""), width = 10, height = 7)

cowplot::plot_grid(q3, q4)
ggsave(paste(rootdir, "/presentation_materials/qplot2.png", sep = ""), width = 14, height = 7)
```