---
title: "WB_HRVS_estimation"
author: "Matthew Gordon"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
rootdir <- dirname(getwd())
```

### Load packages and data

```{r, message=FALSE, echo=FALSE, warning=FALSE}
library(tidyverse)
library(sf)
library(lfe)
library(AER)
library(ggnewscale)
library(cowplot)
library(stargazer)
library(sandwich)
library(readstata13)
#devtools::install_github("mdgordo/rdrobust",ref="master")
library(rdrobust)
library(RDHonest)
#devtools::install_github("mdgordo/dumbells",ref="master")
library(dumbells)
library(rdpower)
library(hdm)
library(boot)
library(parallel)
source(paste(rootdir, "/code/rdhelpers.r", sep = ""))

df.hh <- read_csv(paste(rootdir, "/data/processed/full_panel.csv", sep = ""), guess_max = 7500)
df.hh <- filter(df.hh, !is.na(total_income), !is.na(home_investment), !is.na(productive_assets), 
                !is.na(loan_payments), !is.na(loan_payments_received), !is.na(remittance_income), food_consumption>0) %>%
  mutate(wave2 = if_else(wave==2,1,0),
         wave3 = if_else(wave==3,1,0),
         logloss = log(gorkha_loss_ever+1),
         dist_pos14 = if_else(dist_2_14>0, dist_2_14, 0),
         dist_pos13 = if_else(dist_2_seg13>0, dist_2_seg13, 0),
         dist_pos1 = if_else(dist_2_seg1>0, dist_2_seg1, 0),
         seg14_2 = if_else(border14_segment==2,1,0),
         seg14_3 = if_else(border14_segment==3,1,0),
         seg14_2dist = seg14_2*dist_2_14,
         seg14_3dist = seg14_3*dist_2_14,
         seg14_2distpos = seg14_2*dist_pos14,
         seg14_3distpos = seg14_3*dist_pos14,
         seg13_2 = if_else(border_segment13==2,1,0),
         seg13dist = seg13_2*dist_2_seg13,
         seg13distpos = seg13_2*dist_pos13) %>%
  group_by(hhid) %>%
  mutate(lag_h = lag(home_value, order_by = wave))
```

Define vars

```{r, warning = FALSE}
placebos <- c("elevation", "shake_pga", "gorkha_hh", "gorkha_loss_ever", "high_caste", "age_hh", "highest_ed", "hhmembers",
              "always_lived_house", "always_lived_dist", "slope", "pub_transfers", "NGO_transfers")
infravars <- c("time_to_bank", "time_to_school", "time_to_health", "time_to_market")
pricevars <- c("chicken_price", "rice_price", "lentil_price", "sugar_price", "mutton_price")
aidvars <- c("aid_cumulative_bin", "aid_cumulative", "reconstruction_aid_bin", "reconstruction_aid_cumulative")
mainvars <- c("food_consumption", "home_investment", "total_income", "productive_assets", 
              "remittance_income", "loan_payments", "loan_payments_received", "n_migrants")

### regression specs
de = "none"; kern = "triangular"; takelogs = FALSE; serobust = "hc1"; ctrls = c("shake_pga", "gorkha_loss_ever")
```

#### Regression Discontinuity

### MSE bandwidths and Post double Lasso control selection

```{r, warning = FALSE}
bws <- optbw("reconstruction_aid_bin", b = "dist_2_seg1", df = df.hh, fuzzy = FALSE, vars = ctrls, 
             dist.exclude = de, k = kern, vce = serobust, ihs = FALSE)
h1 <- bws[1,1]
b1 <- bws[1,3]

bws <- optbw("food_consumption", b = "dist_2_seg1", df = df.hh, fuzzy = TRUE, vars = ctrls, 
             dist.exclude = de, k = kern, vce = serobust, ihs = takelogs)
h0 <- bws[1,1]
b0 <- bws[1,3]

saveRDS(h0, paste(rootdir, "/data/model_output/optbw.rds", sep = ""))
```

### regressions

```{r}
df <- dfprep(df.hh, 0, "dist_2_seg13", "none", hpop = 100)

rabmod <- lm(reconstruction_aid_bin ~ shake_pga + gorkha_loss_ever, df.hh)
df.hh$reconstruction_aid_bin_resid <- rabmod$residuals

out <- RDHonest(reconstruction_aid_bin_resid ~ dist_2_seg1, data = df.hh, opt.criterion = "MSE", weights = wt_hh)
out
out <- RDHonest(reconstruction_aid_bin_resid ~ dist_2_seg1, data = df.hh, opt.criterion = "FLCI", weights = wt_hh)
out
out <- RDHonest(reconstruction_aid_bin_resid ~ dist_2_seg1, data = df.hh, opt.criterion = "MSE", weights = wt_hh, kern = "epanechnikov")
out
out <- RDHonest(reconstruction_aid_bin_resid ~ dist_2_seg1, data = filter(df.hh, abs(dist_2_seg1)>5), opt.criterion = "MSE", weights = wt_hh)
out
out <- RDHonest(reconstruction_aid_bin_resid ~ dist_2_seg1, data = df.hh, opt.criterion = "MSE", weights = wt_hh, h = 50)
out
out <- RDHonest(reconstruction_aid_bin_resid ~ dist_2_seg1, data = df.hh, opt.criterion = "MSE", weights = wt_hh, h = 10)
out
```

```{r}
df <- dfprep(df.hh, 0, "dist_2_seg1", "none", hpop = 100)
rabmod <- lm(gorkha_hh ~ shake_pga + gorkha_loss_ever, df.hh)
df.hh$gorkha_hh <- rabmod$residuals

out <- RDHonest(gorkha_hh ~ dist_2_seg1, data = df.hh, opt.criterion = "MSE", weights = wt_hh)
out=
out <- RDHonest(high_caste ~ dist_2_seg1, data = df.hh, opt.criterion = "MSE", weights = wt_hh)
out
out <- RDHonest(age_hh ~ dist_2_seg1, data = df.hh, opt.criterion = "MSE", weights = wt_hh)
out
out <- RDHonest(highest_ed ~ dist_2_seg1, data = df.hh, opt.criterion = "MSE", weights = wt_hh)
out
out <- RDHonest(hhmembers ~ dist_2_seg1, data = df.hh, opt.criterion = "MSE", weights = wt_hh)
out
out <- RDHonest(always_lived_house ~ dist_2_seg1, data = df.hh, opt.criterion = "MSE", weights = wt_hh)
out
out <- RDHonest(pub_transfers ~ dist_2_seg1, data = df.hh, opt.criterion = "MSE", weights = wt_hh)
out
out <- RDHonest(NGO_transfers ~ dist_2_seg1, data = df.hh, opt.criterion = "MSE", weights = wt_hh)
out
```

First stage - uses bandwidth for food consumption (as starting point)

```{r, warnings=FALSE}
dftest <- filter(df.hh, gorkha_hh==1)

rdstg11 <- lapply(aidvars, regout, b = "dist_2_seg1pt", df = df.hh, 
                 dist.exclude = de, vars = ctrls, k = kern, vce = serobust)

rdstg12 <- lapply(aidvars, regout, b = "dist_2_seg1pt", df = df.hh, 
                 dist.exclude = de, vars = ctrls, k = "epanechnikov", vce = serobust)

rdstg13 <- lapply(aidvars, regout, b = "dist_2_seg1pt", df = df.hh,
                h = rdstg11[[1]]$bws[1,1]/2, b0 = rdstg11[[1]]$bws[1,1]/2, 
                 dist.exclude = de, vars = ctrls, k = kern, vce = serobust)

rdstg13a <- lapply(aidvars, regout, b = "dist_2_seg1pt", df = df.hh,
                   h = rdstg11[[1]]$bws[1,1]*2, b0 = rdstg11[[1]]$bws[1,1]*2, 
                 dist.exclude = de, vars = ctrls, k = kern, vce = serobust)

rdstg14 <- lapply(aidvars, regout, b = "dist_2_seg1pt", df = df.hh,
                 dist.exclude = de, vars = ctrls, k = kern, vce = serobust, poly = 2)

rdstg15 <- lapply(aidvars, regout, b = "dist_2_seg1pt", df = df.hh,
                 dist.exclude = de, vars = ctrls, k = kern, vce = serobust, donut = 5)

rdstg1 <- c(rdstg11, rdstg13a, rdstg13a, rdstg14, rdstg15, rdstg12)

rdgazer(rdstg1[c(1:12)], dvlabs = rep(c("Received Aid", "Cumulative Aid", "Recon Aid Bin", "Recon Aid Tot"), 3), type = "text", 
        xlines = list(c("Kernel", rep("triangular", 12)),
                      c("Polynomial", rep("linear", 12)),
                      c("5 km Donut", rep("", 12)),
                      c("Wards", sapply(rdstg1, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))))

rdgazer(rdstg1[c(13:24)], dvlabs = rep(c("Received Aid", "Cumulative Aid", "Recon Aid Bin", "Recon Aid Tot"), 3), type = "text", 
        xlines = list(c("Kernel", rep("triangular", 8), rep("epanechnikov", 4)),
                      c("Polynomial", rep("quadratic", 4), rep("linear", 8)),
                      c("5 km Donut", rep("", 4), rep("X", 4), rep("", 4)),
                      c("Wards", sapply(rdstg1, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))))

```

### Placebo checks - no covariates - optimal bandwidths

```{r}
rdplacebo <- lapply(c(placebos[!placebos%in%c("gorkha_hh","shake_pga", "elevation", "gorkha_loss_ever")], infravars),
                    regout, b = "dist_2_seg1pt", df = dftest, fuzzy = "reconstruction_aid_bin", 
                    dist.exclude = de, vars = "shake_pga", k = kern, vce = serobust)
rdgazer(rdplacebo, dvlabs = str_replace_all(c(placebos[!placebos%in%c("gorkha_hh","shake_pga", "elevation", "gorkha_loss_ever")], infravars), "_", " "), 
        xlines = list(c("Wards", sapply(rdplacebo, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdprice <- lapply(pricevars, regout, b = "dist_2_seg1pt", df = dftest, fuzzy = "reconstruction_aid_bin",  
                  dist.exclude = de, vars = "shake_pga", k = kern, vce = serobust)
rdgazer(rdprice, dvlabs = str_replace_all(pricevars, "_", " "), 
        xlines = list(c("Wards", sapply(rdprice, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

```

### Main Outcomes - log + 1, individualized optimal bandwidths and covariate selection 
Note - optimal covariate selection will not work properly for alternate kernels or borders

```{r, warning=FALSE}
rdmain <- lapply(mainvars, regout, b = "dist_2_seg1pt", df = df.hh, fuzzy = "reconstruction_aid_cumulative",
                 dist.exclude = de, vars = "none", k = kern, vce = serobust, ihs = TRUE)
rdgazer(rdmain, dvlabs = str_replace_all(mainvars, "_", " "), 
        xlines = list(c("Wards", sapply(rdmain, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")
```
### Heterogeneous Effects

```{r}
df <- dfprep(df.hh, 0, "dist_2_seg1", de) %>%
  mutate(kwt = wt_hh*(1-abs(dist_2_seg13)/h0)) %>%
  filter(wave!=1)
form <- as.formula(paste("log(food_consumption) ~ reconstruction_aid_bin + reconstruction_aid_bin:log(landvalue+1) + log(landvalue+1)",
                         " + dist_2_seg1 + ", 
              paste0(ctrls, collapse = "+"), 
              "| dist_14 + dist_14:log(landvalue+1) + log(landvalue+1) + dist_2_seg1 + ", 
          paste0(ctrls, collapse = "+"), sep =""))

reg1 <- ivreg(form, data = df, weights = kwt, 
              subset = abs(dist_2_seg13)<h0)

form <- as.formula(paste("log(home_investment+1) ~ reconstruction_aid_bin + reconstruction_aid_bin:log(landvalue+1) + log(landvalue+1)",
                         " + dist_2_seg1 +", 
              paste0(ctrls, collapse = "+"), 
              "| dist_14 + dist_14:log(landvalue+1) + log(landvalue+1) + dist_2_seg1 + ", 
          paste0(ctrls, collapse = "+"), sep =""))

df <- mutate(df, kwt = wt_hh*(1-abs(dist_2_seg13)/h0))
reg2 <- ivreg(form, data = df, weights = kwt, 
              subset = abs(dist_2_seg13)<h0)

stargazer(reg1, reg2, type = "text", omit = c(ctrls, "dist_2_seg1"))
```

Food Consumption - 100,000 is about $2.7/day, close to the median

```{r, warning = FALSE}
df <- dfprep(df.hh, 0, "dist_2_seg13", de)
cvarscutpts <- quantile(df$food_consumption, seq(.1, .9, .1), na.rm = TRUE)
ctlist <- lapply(cvarscutpts, cutvars, var = "food_consumption", df)
df <- cbind(df, data.frame(do.call(cbind, ctlist)))
ctrls = pdlvarselect("food_consumption", df = df, dist.exclude = de, donut = 0, 
                     k = kern, vce = serobust, ihs = FALSE)
bws <- optbw("food_consumption", b = "dist_2_seg13", df = df.hh, fuzzy = TRUE, vars = "opt", 
             dist.exclude = de, k = kern, vce = serobust, ihs = takelogs)
h0 <- bws[1,1]
b0 <- bws[1,3]

cvarst <- paste("t", cvarscutpts, sep = "")
cvarsu <- paste("u", cvarscutpts, sep = "")
cvarsc <- paste("c", cvarscutpts, sep = "")

rdc <- lapply(cvarst, regout, b = "dist_2_seg13", df = df, fuzzy = TRUE, vars = ctrls, h = h0, b0 = b0, 
              k = kern, vce = serobust, dist.exclude = de, ihs = FALSE)
rdgazer(rdc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcu <- lapply(cvarsu, regout, b = "dist_2_seg13", df = df, fuzzy = "inv", vars = ctrls, h = h0, b0 = b0, 
               k = kern, vce = serobust, dist.exclude = de)
rdgazer(rdcu, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcu, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcc <- lapply(cvarsc, regout, b = "dist_2_seg13", df = df, fuzzy = TRUE, vars = ctrls, h = h0, b0 = b0, 
               k = kern, vce = serobust, dist.exclude = de)
rdgazer(rdcc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

foodt <- unlist(lapply(rdc, function(x) x$Estimate[1]))
foodu <- unlist(lapply(rdcu, function(x) x$Estimate[1]))
foodRD <- list(foodt, foodu, cvarscutpts)
saveRDS(foodRD, paste(rootdir, "/data/model_output/foodRD.rds", sep = ""))
```


```{r, warning=FALSE}
q1 <- qplot("food_consumption", df, grid = NULL, fuzzy = TRUE, vars = ctrls, h = h0, b = b0, 
              k = kern, vce = serobust, dist.exclude = de, ihs = FALSE) +
  theme(text = element_text(size = 20)) + labs(x = "Food Consumption", y = "P(X<x)", color = "Aid")
q1
#ggsave(paste(rootdir, "/presentation_materials/qplot_food.png", sep = ""), width = 10, height = 7)
```

```{r, warning = FALSE}
df <- dfprep(df.hh, 0, "dist_2_seg13", de)
cvarscutpts <- quantile(df$home_investment, c(.5, .75, .9, .95, .99), na.rm = TRUE)
ctlist <- lapply(cvarscutpts, cutvars, var = "home_investment", df)
df <- cbind(df, do.call(cbind, ctlist))
ctrls = pdlvarselect("home_investment", df = df, dist.exclude = de, donut = 0, 
                     k = kern, vce = serobust, ihs = FALSE)
bws <- optbw("home_investment", b = "dist_2_seg13", df = df.hh, fuzzy = TRUE, vars = "opt", 
             dist.exclude = de, k = kern, vce = serobust, ihs = takelogs)
h0 <- bws[1,1]
b0 <- bws[1,3]

cvarst <- paste("t", cvarscutpts, sep = "")
cvarsu <- paste("u", cvarscutpts, sep = "")
cvarsc <- paste("c", cvarscutpts, sep = "")

rdc <- lapply(cvarst, regout, b = "dist_2_seg13", df = df, fuzzy = TRUE, vars = ctrls, h = h0, b0 = b0,
              k = kern, vce = serobust, dist.exclude = de, ihs = FALSE)
rdgazer(rdc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcu <- lapply(cvarsu, regout, b = "dist_2_seg13", df = df, fuzzy = "inv", vars = ctrls, h = h0, b0 = b0,
               k = kern, vce = serobust, dist.exclude = de)
rdgazer(rdcu, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcu, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcc <- lapply(cvarsc, regout, b = "dist_2_seg13", df = df, fuzzy = TRUE, vars = ctrls, h = h0, b0 = b0,
               k = kern, vce = serobust, dist.exclude = de)
rdgazer(rdcc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

foodt <- unlist(lapply(rdc, function(x) x$Estimate[1]))
foodu <- unlist(lapply(rdcu, function(x) x$Estimate[1]))
foodRD <- list(foodt, foodu, cvarscutpts)
saveRDS(foodRD, paste(rootdir, "/data/model_output/foodRD.rds", sep = ""))
```

```{r, warning = FALSE}
df <- dfprep(df.hh, 0, "dist_2_seg13", de)
cvarscutpts <- quantile(df$total_outlays_net, seq(.1, .9, .1), na.rm = TRUE)
ctlist <- lapply(cvarscutpts, cutvars, var = "total_outlays_net", df)
df <- cbind(df, do.call(cbind, ctlist))
ctrls = pdlvarselect("total_outlays_net", df = df, dist.exclude = de, donut = 0, 
                     k = kern, vce = serobust, ihs = FALSE)
bws <- optbw("total_outlays_net", b = "dist_2_seg13", df = df.hh, fuzzy = TRUE, vars = "opt", 
             dist.exclude = de, k = kern, vce = serobust, ihs = takelogs)
h0 <- bws[1,1]
b0 <- bws[1,3]

cvarst <- paste("t", cvarscutpts, sep = "")
cvarsu <- paste("u", cvarscutpts, sep = "")
cvarsc <- paste("c", cvarscutpts, sep = "")

rdc <- lapply(cvarst, regout, b = "dist_2_seg13", df = df, fuzzy = TRUE, vars = ctrls, h = h0, b0 = b0,
              k = kern, vce = serobust, dist.exclude = de, ihs = FALSE)
rdgazer(rdc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcu <- lapply(cvarsu, regout, b = "dist_2_seg13", df = df, fuzzy = "inv", vars = ctrls, h = h0, b0 = b0,
               k = kern, vce = serobust, dist.exclude = de)
rdgazer(rdcu, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcu, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcc <- lapply(cvarsc, regout, b = "dist_2_seg13", df = df, fuzzy = TRUE, vars = ctrls, h = h0, b0 = b0,
               k = kern, vce = serobust, dist.exclude = de)
rdgazer(rdcc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

foodt <- unlist(lapply(rdc, function(x) x$Estimate[1]))
foodu <- unlist(lapply(rdcu, function(x) x$Estimate[1]))
foodRD <- list(foodt, foodu, cvarscutpts)
saveRDS(foodRD, paste(rootdir, "/data/model_output/foodRD.rds", sep = ""))
```

```{r, warning = FALSE}
df <- dfprep(df.hh, 0, "dist_2_seg13", de)
cvarscutpts <- quantile(df$total_income, seq(.1, .9, .1), na.rm = TRUE)
ctlist <- lapply(cvarscutpts, cutvars, var = "total_income", df)
df <- cbind(df, do.call(cbind, ctlist))
ctrls = pdlvarselect("total_income", df = df, dist.exclude = de, donut = 0, 
                     k = kern, vce = serobust, ihs = FALSE)
bws <- optbw("total_income", b = "dist_2_seg13", df = df.hh, fuzzy = TRUE, vars = "opt", 
             dist.exclude = de, k = kern, vce = serobust, ihs = takelogs)
h0 <- bws[1,1]
b0 <- bws[1,3]

cvarst <- paste("t", cvarscutpts, sep = "")
cvarsu <- paste("u", cvarscutpts, sep = "")
cvarsc <- paste("c", cvarscutpts, sep = "")

rdc <- lapply(cvarst, regout, b = "dist_2_seg13", df = df, fuzzy = TRUE, vars = ctrls, h = h0, b0 = b0,
              k = kern, vce = serobust, dist.exclude = de, ihs = FALSE)
rdgazer(rdc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcu <- lapply(cvarsu, regout, b = "dist_2_seg13", df = df, fuzzy = "inv", vars = ctrls, h = h0, b0 = b0,
               k = kern, vce = serobust, dist.exclude = de)
rdgazer(rdcu, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcu, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

rdcc <- lapply(cvarsc, regout, b = "dist_2_seg13", df = df, fuzzy = TRUE, vars = ctrls, h = h0, b0 = b0,
               k = kern, vce = serobust, dist.exclude = de)
rdgazer(rdcc, dvlabs = paste("<", round(cvarscutpts/1000,0), "k npr", sep = ""), 
        xlines = list(c("Wards", sapply(rdcc, function(x) length(unique(x$X[abs(x$X)<x$bws[2,1]]))))), type = "text")

foodt <- unlist(lapply(rdc, function(x) x$Estimate[1]))
foodu <- unlist(lapply(rdcu, function(x) x$Estimate[1]))
foodRD <- list(foodt, foodu, cvarscutpts)
saveRDS(foodRD, paste(rootdir, "/data/model_output/foodRD.rds", sep = ""))
```

### RD plots
need to filter out hhs > than 100km because otherwise cross into otherside of border
Clean versions:

```{r}
df.plot1 <- filter(df.hh, abs(dist_2_seg1)<150)
plotlist <- lapply(aidvars, plotvar, b = "dist_2_seg1", df = df.plot1, dist.exclude = de, vars = "none", p = 4)
plotlist
```


```{r}
plotlist <- lapply(placebos, plotvar, b = "dist_2_seg13", df = df.plot1, dist.exclude = de, vars = "none", p = 4)
plotlist

```

```{r}
plotlist <- lapply(mainvars, plotvar, b = "dist_2_seg1", df = df.plot1, dist.exclude = de, vars = "none", p = 4)
plotlist
```
### Residualized

```{r}
residualizer <- function(varname){
  df.plot1 <- filter(df.plot1, !is.na(get(varname)))
  resreg1 <- lm(get(varname) ~ shake_pga + gorkha_loss_ever,
              data = df.plot1)
  df.plot1$lossresid <- resreg1$residuals
  plotvar("lossresid", b = "dist_2_seg1", df = df.plot1, dist.exclude = de, vars = "none", p = 1) +
    labs(y = varname)
}

lapply(aidvars, residualizer)
```

```{r}
lapply(placebos, residualizer)
```

```{r}
lapply(mainvars, residualizer)
```


```{r}
bws <- optbw("pub_transfers", b = "dist_2_seg1", df = df.hh, fuzzy = FALSE, vars = "shake_pga")
h0 <- bws[1,1]; b0 <- bws[1,3]

df <- filter(df.hh, designation %in% c("severe", "crisis", "heavy")) %>%
  mutate(kwt = wt_hh*(1-abs(dist_2_seg13)/60)) 

reg1 <- ivreg(gorkha_hh ~ reconstruction_aid_bin + dist_2_seg1 + dist_pos1 + gorkha_loss_ever + shake_pga |
                dist_14 + dist_2_seg1 + dist_pos1 + gorkha_loss_ever + shake_pga , data = df, weights = kwt, 
              subset = abs(dist_2_seg13)<20)
coeftest(reg1, type = "hc1")
placebos
```

### Functions for Mccrary test
Discrete version based on: https://cattaneo.princeton.edu/aie-rdd/Frandsen_2016_AIE.pdf
Sampling frame based on 2010 census - need to adjust to hhs per unit area

```{r}
mcplot <- histfunc("dist_2_seg13", filter(df.hh, wave==1), h = h0, dist.exclude = "none")

mcplot + labs(x = "distance to border") + theme(text = element_text(size = 20))
ggsave(paste(rootdir, "/presentation_materials/mccrary.png", sep = ""), width = 10, height = 7)
```


Power calculations - uses optimal bandwidths and covs for food consumption

```{r, warning = FALSE}
df.pow <- filter(df.hh, !is.na(consumption) & designation!="none", 
                 !is.na(high_caste), !is.na(class5), !is.na(age_hh), !is.na(gorkha_hh), !is.na(slope), !is.na(elevation))
powcovs <- covmatmaker("dist_2_seg13", df.pow, vars = pdlvarselect("food_consumption"))

print("First Stage")
a <- rdpower(data = cbind(df.pow$aid_cumulative_bin, df.pow$dist_2_seg13), k = kern, vce = serobust, 
        covs =  powcovs, cluster = df.pow$strata, weights = df.pow$wt_hh)
print("Consumption")
a <- rdpower(data = cbind(log(df.pow$food_consumption+1), df.pow$dist_2_seg13), k = kern, vce = serobust, 
        covs =  powcovs, cluster = df.pow$strata, weights = df.pow$wt_hh)
print("Consumption w IV")
a <- rdpower(data = cbind(log(df.pow$food_consumption+1), df.pow$dist_2_seg13), k = kern, vce = serobust,  
        covs =  powcovs, cluster = df.pow$strata, weights = df.pow$wt_hh, fuzzy = df.pow$received_aid)
```


```{r}
b = boot(df, earthmovers, R = 1000, cutpts = cvarscutpts, weights = df$wt_hh, strata = df$strata, 
         parallel = "multicore", ncpus = detectCores() - 2)
b$t0
boot.ci(b, type = "perc", conf = c(.9, .95, .99))
```


